About

### 2021-03-11 analysis/about.Rmd
workflowr::wflow_publish("analysis/about.Rmd")
about.Rmd

Please note that this project was built with R version 4.0.3 on a CentOS 7 operating system.
Some packages from this project **are not compatible with R versions prior version 3.6.0.**

@@

-   `bm_aggregated_new_buffer2`: Aggregated benchmark results of all models using a 2 meter buffer for hyperspectral data extraction.
-   `eda_wfr`: Creates the [report which shows Exploratory Data Analysis (EDA) plots and tables](https://pat-s.github.io/2019-feature-selection/eda.html).
-   `eval_performance_wfr`: Creates the [report which evaluates the model performances](https://pat-s.github.io/2019-feature-selection/eval-performance.html).
-   `spectral_signatures_wfr`: Creates the [report which inspects the spectral signatures of the hyperspectral data](https://pat-s.github.io/2019-feature-selection/spectral-signatures.html).
-   `feature_importance_wfr`: Creates the [report which inspects the feature importance of variables](https://pat-s.github.io/2019-feature-selection/feature-importance.html).
-   `filter_correlations_wfr`: Creates the [report which inspects correlations among filter methods](https://pat-s.github.io/2019-feature-selection/feature-importance.html).

Note that most reports require some/all fitted models.
Creating these (e.g. target `benchmark_no_models_new_buffer2`) is a costly process and takes several days on a HPC and way longer on a single machine.

>>>>

Please note that this project was built with R version 4.0.4 on a CentOS 7 operating system.
Some packages from this project **are not compatible with R versions prior version 3.6.0.**

@@

-   `bm_aggregated`: Aggregated benchmark results of all models using a 1 meter buffer for hyperspectral data extraction.
-   `eda_wfr`: Creates the [report which shows Exploratory Data Analysis (EDA) plots and tables](https://pat-s.github.io/2019-feature-selection/eda.html).
-   `eval_performance_wfr`: Creates the [report which evaluates the model performances](https://pat-s.github.io/2019-feature-selection/eval-performance.html).
-   `spectral_signatures_wfr`: Creates the [report which inspects the spectral signatures of the hyperspectral data](https://pat-s.github.io/2019-feature-selection/spectral-signatures.html).
-   `feature_importance_wfr`: Creates the [report which inspects the feature importance of variables](https://pat-s.github.io/2019-feature-selection/feature-importance.html).
-   `filter_correlations_wfr`: Creates the [report which inspects correlations among filter methods](https://pat-s.github.io/2019-feature-selection/feature-importance.html).

Note that most reports require some/all fitted models.
Creating these (e.g. target `benchmark_no_models`) is a costly process and takes several days on a HPC and way longer on a single machine.
